\thesistitle

### 2019-06-16 sections/research.tex
Better formulas

$$T2R\ Variability\ Percentage=\frac{Diff(l) + Diff(v) + Diff(m)}{Total(t)}*100$$
$$Diff=Amount\ that\ differ\ from\ other\ clone\ instances\ in\ the\ clone\ class$$
$$Total\ =\ Total\ number\ in\ the\ clone\ instance$$
$$l=Number\ of\ literals$$
$$v=Number\ of\ variables$$
$$m=Number\ of\ method\ calls$$
$$t=Number\ of\ tokens$$

@@

\section{Type 3R clones}
Type 3 clones allow any change in statements, often bounded by a similarity threshold. This means that type 3R allows the inclusion of a statement that is not detected by type 1 or 2 clone detection. When looking at how we can refactor a statement that is not included by one clone instance but is in another, we find that we require a conditional block to make up for the difference in statements. See figure \ref{fig:type3} for an example of such a clone.

>>>>

$$\text{T2R Variability Percentage}=\frac{Diff(l) + Diff(v) + Diff(m)}{Total(t)}*100$$
$$\text{Diff = Amount that differ from other clone instances in the clone class}$$
$$\text{Total = Total number in the clone instance}$$
$$\text{l = Number of literals}$$
$$\text{v = Number of variables}$$
$$\text{m = Number of method calls}$$
$$\text{t = Number of tokens}$$

@@

\subsection{Type 3R clones}
Type 3 clones allow any change in statements, often bounded by a similarity threshold. This means that type 3R allows the inclusion of a statement that is not detected by type 1 or 2 clone detection. When looking at how we can refactor a statement that is not included by one clone instance but is in another, we find that we require a conditional block to make up for the difference in statements. See figure \ref{fig:type3} for an example of such a clone.
